Something something values disclosure replication

### 2022-07-06 paper/paper.Qmd
latex issues

Next, we tested the hypotheses that (H2) scientists who find a chemical harms human health are perceived as more trustworthy than scientist who find that a chemical does not cause harm and (H3) a scientist who discloses values are perceived as less trustworthy than a scientist who does not. For this analysis, we regressed participants' METI ratings onto both the Conclusions and Disclosure experimental conditions. The full model was significant, adj. R^2 = .148, F(2, 985) = 86.59, p < .001 (see @tbl-bc). Specifically, results revealed that the conclusions reported by the scientist predicted participants' perceived trustworthiness in line with our hypothesis. Participants rated the scientist who reported that BPA causes harm as more trustworthy than the scientist who reported that BPA does not cause harm. By contrast, the results do not provide evidence in favor of our hypothesis that a scientist disclosing their values are perceived as less trustworthy than a scientist who does not disclose values.

@@

H5b - consumer risk sensitivity
To test whether the findings regarding consumer risk sensitivity vary as a function of participants' values, we regressed participants' METI ratings of the scientist in the stimuli onto the Conclusions condition, Participants' Values variable, and the Conclusions by Participants' values interaction term. The full model was significant, adj. R^2 = .173, F(3, 840) = 59.95, p < .001 [@tbl-eb model 2]. As with the earlier analysis, results showed a main effect of the Conclusions condition, such that participants rated the scientist who reported that BPA causes harm as more trustworthy than the scientist who reported that BPA does not cause harm. However, this effect was qualified by a significant interaction with participants' values. *[is this right? Participants who prioritized public health over economic growth and read about a scientist who concluded that BPA causes harm rated the scientist as more trustworthy than participants who read about a scientist who concluded that BPA does not cause harm, regardless of those participants' values.]*

@@

H5c - transparency penalty
To test whether the findings above about a hypothesized transparency penalty may vary based on participants' values, we regressed participants' METI ratings of the scientist onto the Disclosure condition variable, Participants' Values variable, and the Disclosure by Participants' Values interaction term. The full model was not significant, adj. R^2 < .001, F(3, 840) = 1.19, p = .31 [@tbl-ec model 2]. As with the earlier analysis, our results do not provide evidence for a transparency penalty to the perceived trustworthiness of a scientist, either in general or interacting with participants' own reported values.

>>>>

Next, we tested the hypotheses that (H2) scientists who find a chemical harms human health are perceived as more trustworthy than scientist who find that a chemical does not cause harm and (H3) a scientist who discloses values are perceived as less trustworthy than a scientist who does not. For this analysis, we regressed participants' METI ratings onto both the Conclusions and Disclosure experimental conditions. The full model was significant, adj. R^2 = .148, F(2, 985) = 86.59, p < .001 (see @tbl-bc). Specifically, results revealed that the conclusions reported by the scientist predicted participants' perceived trustworthiness in line with our hypothesis. Participants rated the scientist who reported that BPA does not cause harm as less trustworthy ($M_{sd} = 4.48_{1.26}$) than the scientist who reported that BPA causes harm ($M_{sd} = 5.47_{1.12}$), $\beta$ = -0.99, t(985) = -13.09, p < .001. By contrast, the results do not provide evidence in favor of our hypothesis that a scientist disclosing their values ($M_{sd} = 4.94_{1.33}$) are perceived as less trustworthy than a scientist who does not disclose values  ($M_{sd} = 5.05_{1.21}$), $\beta$ = -0.12, t(985) = -1.46, p = .143.

@@

H5b - consumer risk sensitivity
To test whether the findings regarding consumer risk sensitivity vary as a function of participants' values, we regressed participants' METI ratings of the scientist in the stimuli onto the Conclusions condition, Participants' Values variable, and the Conclusions by Participants' values interaction term. The full model was significant, adj. R^2 = .173, F(3, 840) = 59.95, p < .001 [@tbl-eb model 2]. As with the earlier analysis, results showed a main effect of the Conclusions condition, such that participants rated the scientist who reported that BPA does not cause harm as less trustworthy than the scientist who reported that BPA causes harm, $\beta$ = -0.75, t(840) = -4.51, p < .001. However, this effect was qualified by a significant interaction with participants' values, $\beta$ = -0.41, t(840) = -2.16, p = .031. *[is this right? Participants who prioritized public health over economic growth and read about a scientist who concluded that BPA causes harm rated the scientist as more trustworthy ($M_{sd} = 5.56_{1.09}$) than participants who read about a scientist who concluded that BPA does not cause harm, regardless of those participants' values ($M_{sd} = 4.63_{1.22}$) for participants who prioritized economic growth and ($M_{sd} = 4.40_{1.24}$) for participants who prioritized public health].]* Further, participants who prioritized public health over economic growth reading and read about a scientist who concluded that BPA does not cause harm rated the scientist as less trustworthy ($M_{sd} = 4.40_{1.24}$) than participants who read about a scientist who concluded that BPA does cause harm, regardless of those participants' values ($M_{sd} = 5.39_{1.15}$) for participants who prioritized economic growth; $M_{sd} = 5.56_{1.09}$ for participants who prioritized public health).

@@

H5c - transparency penalty
To test whether the findings above about a hypothesized transparency penalty may vary based on participants' values, we regressed participants' METI ratings of the scientist onto the Disclosure condition variable, Participants' Values variable, and the Disclosure by Participants' Values interaction term. The full model was not significant, adj. R^2 < .001, F(3, 840) = 1.19, p = .31 [@tbl-ec model 2]. As with the earlier analysis, our results do not provide evidence for a transparency penalty to the perceived trustworthiness of a scientist, either in general or interacting with participants' own reported values, $\beta$ = -0.23, t(840) = -1.07, p = 0.286.
